Predicting sales of newly published books

### 2015-08-21 paper.tex
completando el estado del arte
comentando los resultados obtenidos con cada método, tanto en cuanto al tiempo como en cuanto al error

A company that intends to release a new product has a high risk due to
the complexity of the production and distribution processes. A newly
% tienes que enmarcar el problema. Se trata de productos culturales
% con soporte físico y con ventas relativamente pequeñas. Libros,
% discos, no sé si alguna cosa más. - JJ
launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sale predictions 
(a reduction of forecasting errors) results in an improvement in the 
production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

@@

In classification problems the algorithm searchs for an optimal hyperplane 
that separates two classes, maximizing the margin between two classes. 
In the case of regression the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimizing the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples 
(called support vectors).

@@

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
Obtained results using the different forecasting methods on the dataset with 7 
variables per book can be shown in Table \ref{tabla:results7}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)     & MAE       & RMSE    & RAE (\%)     & RRSE (\%)      \\
\hline
  MP5     & 7.77 $\pm$ 1.15   & 117.78   & 260.05  & 18.51   & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41 & 120.29  & 252.91  & 18.91   & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50 & 109.30  & 251.16   & 17.18     & 16.42   \\
\hline
  KNN     & 0.03 $\pm$ 0.01   & 293.98  & 1071.52  & 46.21   & 70.06   \\
\hline
  MLP     & 3646.76 $\pm$ 64.83   & 705.69 $\pm$ 77.22   & 1608.69 $\pm$ 42.96  & 110.92 $\pm$ 12.14   & 105.18 $\pm$ 2.81   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7}
\end{table*}

\textbf{TODO: FALTA COMENTAR LOS RESULTADOS OBTENIDOS CON LOS 5 MÉTODOS.}

% - indicar qué método da mejores resultados
% - indicar qué método es tipo "caja-negra" y cuáles ofrecen modelos "explicables"
% - 
% -

@@

The most relevant variables when predicting sales have been determined, 
while unrelated or superfluous ones have been removed, 
and sales predictions have been obtained using five different forecasting 
standard methods.
Proposed method was validated by the company and incorporated in a business 
intelligence tool for publishing houses.

In this sense, the decision trees proved to be a suitable model because of the ease 
to explain how the prediction is obtained from the variables that describe the new book. 
This, compared to the black-box models such as the ANN was decisive from the point 
of view of the needs of experts and the company.

This research provides a new direction in the sales forecasting area using 
different soft-computing techniques.
Moreover, proposed method could be implemented, not only in the editorial 
industry, but also in other domains where the specificity of products is similar, 
and might be of interest to other academic researches and industrial practitioners.

@@

As future work, it would be interesting comparing the obtained forecasting results 
with other methods based on soft-computing, such as genetic programming or fuzzy logic.

>>>>

A company that intends to release a new product has a high risk due to
the complexity of the production and distribution processes. 
% tienes que enmarcar el problema. Se trata de productos culturales
% con soporte físico y con ventas relativamente pequeñas. Libros,
% discos, no sé si alguna cosa más. - JJ
A newly launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sale predictions 
(a reduction of forecasting errors) results in an improvement in the 
production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

@@

In classification problems the algorithm searchs for an optimal hyperplane 
that separates two classes, maximizing the margin between two classes. 
In the case of regression the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimizing the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples 
(called support vectors).
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

@@

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
Obtained results using the different forecasting methods on the dataset with 7 
variables per book can be shown in Table \ref{tabla:results7}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  MP5     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  KNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3646.76 $\pm$ 64.83 & 705.69 $\pm$ 77.22   & 1608.69 $\pm$ 42.96  & 110.92 $\pm$ 12.14   & 105.18 $\pm$ 2.81   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7}
\end{table*}

% - indicar pros y contras de los diferentes métodos
% - indicar qué método da mejores resultados
% - indicar qué método es tipo "caja-negra" y cuáles ofrecen modelos "explicables"

M5P model obtained good results, both in time and error, and as stated before, 
this method can learn and tackle tasks with high dimensionality
and it generates reproducible and comprehensible representations that provide 
information on the decision process and does not require human intervention 
either for the operation or for interpretation. Thus, it is very suitable in 
order to be incorporated in a publishing company processes.

The Linear Regression model outperforms other complex methods, both in time 
(as it is a simple method to train) and in obtained errors.
However, more powerful models, that obtain better results, can be obtained in 
comparable time.

Taking into account the SVM model obtained results, this method obtains the best
errors. Even when used using the default parameter values it exhibit a good 
generalization performance.
However, it is much slower than the others to build the model, not only when 
using the data set with 13 input variables, but when using the data set with 
7 input variables (including \emph{EDITORIAL} and \emph{MATTER}).

kNN is the faster method used in this study, as it is the simpler method.
However, the model is slow when classifying (as there are a large number of 
training examples), and it exhibit a poor generalization ability, as it does not 
learn anything from the training data.

As far as the Multilayer Perceptron, its main drawbacks are both the cost of model 
building (not only parameter and weights setting, but also time to train the 
network) and the fact that it is a back-box model, and thus, it is difficult 
to explain how the forecasts are obtained.
In these experiments, the MLP requires a higher time than other methods, but also
the obtained errors are worse as no parameter tuning to build the models have
been carried out.
Also, the difficulty to process information related to variables \emph{EDITORIAL} 
and \emph{MATTER} might affect the worse results obtained on the final dataset.

Finally, paying attention to the cost in time to obtain the forecasting models 
and their accuracy, the M5P model is the most adequate to solve the problem of 
how many books should be printed when a new book is published.
This forecasting method, as an additional advantage, can be used for products 
with historical sales data and for new products with little or no historical 
data available.

@@

The most relevant variables when predicting sales have been determined, 
while unrelated or superfluous ones have been removed, 
and sales predictions have been obtained using five different forecasting 
standard methods.
Not only the obtained forecasting error has been taking into account to evaluate
those methods, but also the the cost of model building as parameter setting and 
the required time to train the model.

In this sense, the decision trees proved to be a suitable model because of the 
ease to explain how the prediction is obtained from the variables that describe 
the new book. 
This, compared to the black-box models such as the artificial neural network 
was decisive from the point of view of the needs of experts and the company.
Moreover, proposed method was validated by the company and incorporated in a 
business intelligence tool for publishing houses.

Overall, this study contributes to the literature by proposing the use of different 
soft-computing standard techniques to solve a new challenging problem.
Moreover, proposed method could be implemented, not only in the editorial 
industry, but also in other domains where the specificity of products is similar, 
and might be of interest to other academic researches and industrial practitioners.

@@

As future work, it would be interesting comparing the obtained forecasting results 
with other methods based on soft-computing, such as genetic programming or fuzzy logic.
Moreover, as default parameters have been used for proposed forecasting methods,
it would be of interest carrying out some parameter tuning procedure in order to
improve obtained results.
